### 2021-08-16 Manuscript.Rmd
Updated reference to R and packages
Still won't compile due to negative variances though
Deleted automatic bib creation

r_refs("r_references.bib") # creates bib to cite the used R packages

@@

## Data analysis
We used `r cite_r("r_references.bib")` for all our analyses.

>>>>

@@

## Data analysis
We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *lavaan* [@Rosseel2012] and *psych* [@Revelle2021] for all our analyses.
